nospace_10000

### 2021-10-15 graphs_newt_snakes/nospce_10000.Rmd
I was looking at what happens to beta as you change things like mu and sigma in the slim simulation. It is very hard to tell what is going on. I am also trying to look at the 3000gen data. I also made some more msprime files to make newts more adv than snakes.
I ran and looked at the data from the spatial simulation that ran to 3000gen. I want to compair it to the nospace 10000gen simulations.

# Files for space results
files_u5 <- list.files(path="~/Desktop/beta_u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)

beta_n_s <- making_data_frames(files_u5, all_of("beta_n"))
beta_s_s <- making_data_frames(files_u5, all_of("beta_s"))
Newt_mean_Pheno_s <- making_data_frames(files_u5, all_of("Newt_mean_Pheno"))
Snake_mean_Pheno_s <- making_data_frames(files_u5, all_of("Snake_mean_Pheno"))
Newt_sd_Pheno_s <- making_data_frames(files_u5, all_of("Newt_sd_Pheno"))
Snake_sd_Pheno_s <- making_data_frames(files_u5, all_of("Snake_sd_Pheno"))
mean_newts_eaten_s <- making_data_frames(files_u5, all_of("mean_newts_eaten"))
mean_snakes_eaten_s <- making_data_frames(files_u5, all_of("mean_snakes_eaten"))
newt_deaths_s <- making_data_frames(files_u5, all_of("newt_deaths"))
snake_deaths_s <- making_data_frames(files_u5, all_of("snake_deaths"))
Newt_age_s <- making_data_frames(files_u5, all_of("Newt_age"))
Snake_age_s <- making_data_frames(files_u5, all_of("Snake_age"))
Newt_pop_size_s <- making_data_frames(files_u5, all_of("Newt_pop_size"))
Snake_pop_size_s <- making_data_frames(files_u5, all_of("Snake_pop_size"))

>>>>

# Files for space results
files_u5 <- list.files(path="~/Desktop/run_longer/gen_3000/u5", pattern="nu_*1.56", full.names=TRUE, recursive=FALSE)
file <- read.table(files_u5[51], header = TRUE)
beta_n_s <- making_data_frames(files_u5, all_of("beta_n"))
beta_s_s <- making_data_frames(files_u5, all_of("beta_s"))
Newt_mean_Pheno_s <- making_data_frames(files_u5, all_of("Newt_mean_Pheno"))
Snake_mean_Pheno_s <- making_data_frames(files_u5, all_of("Snake_mean_Pheno"))
Newt_sd_Pheno_s <- making_data_frames(files_u5, all_of("Newt_sd_Pheno"))
Snake_sd_Pheno_s <- making_data_frames(files_u5, all_of("Snake_sd_Pheno"))
mean_newts_eaten_s <- making_data_frames(files_u5, all_of("mean_newts_eaten"))
mean_snakes_eaten_s <- making_data_frames(files_u5, all_of("mean_snakes_eaten"))
newt_deaths_s <- making_data_frames(files_u5, all_of("newt_deaths"))
snake_deaths_s <- making_data_frames(files_u5, all_of("snake_deaths"))
Newt_age_s <- making_data_frames(files_u5, all_of("Newt_age"))
Snake_age_s <- making_data_frames(files_u5, all_of("Snake_age"))
Newt_pop_size_s <- making_data_frames(files_u5, all_of("Newt_pop_size"))
Snake_pop_size_s <- making_data_frames(files_u5, all_of("Snake_pop_size"))
